Reconstructing Propositional Proofs in Type Theory

### 2017-11-14 paper/sections/introduction.tex

Previous studies have reported proof-reconstruction using
proof-assistants based on higher-order logic where the development is
at a mature
stage~\cite{paulson2010three,hurlin07practical,kaliszyk2013}. Another
approaches has been proposed for proof-reconstructing based on type
theory~\cite{Bezem2002,kanso2016light,Keller2013}.

@@

The source code accompanying this paper (programs, libraries, and
examples) is available at \verb!GitHub!:
\begin{itemize}
  \item The \Athena program that translates proofs generated by \Metis to \Agda:
  \url{http://github.com/jonaprieto/athena}.
  \item The \verb!agda-prop! library as a formalization in \Agda for
    classical propositional logic:
  \url{http://github.com/jonaprieto/agda-prop}.
\item The \verb!agda-metis! library as a formalization in \Agda to
  justify \Metis proofs of classical propositional logic:
  \url{http://github.com/jonaprieto/agda-prop}.
\end{itemize}
The proof-reconstruction was carried on for \Metis~2.3
(release~20170822), and the programs and libraries were tested with
\Agda~2.5.3, \Agda standard library~0.14, and \prg{GHC}~8.2.1.
\end{document}

>>>>

Previous studies have reported proof-reconstruction using
proof-assistants based on higher-order logic where the development is
at a mature
stage~\cite{paulson2010three,hurlin07practical,kaliszyk2013}. Another
approaches has been proposed for proof-reconstructing based on type
theory in~\cite{Bezem2002,kanso2016light,Keller2013}.

@@

The source code accompanying this paper (programs, libraries, and
examples) is available at \verb!GitHub!:
\begin{itemize}
  \item The \Athena program that translates proofs generated by \Metis to \Agda:
  \url{http://github.com/jonaprieto/athena}.
  \item The \verb!agda-prop! library as a formalization in \Agda for
    classical propositional logic:
  \url{http://github.com/jonaprieto/agda-prop}.
\item The \verb!agda-metis! library as a formalization in \Agda to
  justify \Metis proofs of classical propositional logic:
  \url{http://github.com/jonaprieto/agda-prop}.
\end{itemize}

We carried out proof-reconstruction for \Metis~2.3
(release~20170822). The \Athena program was tested with \prg{GHC}~8.2.1.
The \verb!agda-prop! and \verb!agda-metis! libraries were tested with
\Agda~2.5.3 and \Agda standard library~0.14.

\end{document}

### 2017-11-14 paper/sections/proof-reconstruction/strip.tex
[ paper ] fixed typo in strip.

In a similar way as we define $\fuh_{cm}$ in~\eqref{eq:uh-complexity}, we define
$\fstrip_{cm}$ as the complexity measure for the $\fstrip₀$ function.
Then we define the \fstrip function is defined as follows.
\begin{align}
  \label{eq:strip}
  \begin{split}
  &\fstrip : \Prop → \Prop\\
  &\fstrip~φ~ = \fstrip_{1}~φ~(\fstrip_{cm}~φ).
  \end{split}
\end{align}

@@

\begin{proof}
The proof is by induction on the structure of the
formula~$φ$ by following the equations in~\eqref{eq:strip-fixed}.
We present a straightforward case with double negation, a case with
conjunction connective, and last, the case with a negated disjunction.
We refer the reader to~\cite{AgdaMetis} for the complete proof in \Agda.

>>>>

In a similar way as we define $\fuh_{cm}$ in~\eqref{eq:uh-complexity}, we
define $\fstrip_{cm}$ as the complexity measure for the $\fstrip₀$ function.
Then we define the \fstrip function as follows in~\ref{eq:strip}.

\begin{align}
  \label{eq:strip}
  \begin{split}
  &\fstrip : \Prop → \Prop\\
  &\fstrip~φ~ = \fstrip_{1}~φ~(\fstrip_{cm}~φ).
  \end{split}
\end{align}

@@

\begin{proof}
The proof is by induction on the structure of the
formula~$φ$ by following the equations in~\eqref{eq:strip-fixed}.
We present a straightforward case with double negation, the case for
conjunctions, and last, the case for a negated disjunction.
We refer the reader to~\cite{AgdaMetis} for the complete proof in \Agda.
